Figures

### 2016-01-18 scripts/figures.Rmd

  #plot the roc
  roc.p<-ggplot(roc.df,aes(x=1-specificity,y=sensitivity))+geom_step(color="black",size=2)+xlab("1-Specificity")+ylab("Sensitivity")+theme(axis.title.y=element_text(vjust=1))
  roc.p<-roc.p+geom_line(data=lines,aes(x=spec,y=sense,color=as.factor(group)),size=c(1.5),lty=c(2))+scale_color_brewer(palette="Set1")

@@

}
plot.ex(0.35,0.95,roc.df,example)
pdf("~/Box Sync/Lab_work/Talks/2016_812/figures/roc.ex.pdf")
plot.ex(0.35,0.95,roc.df,example)
dev.off()

@@

miseq.roc.p<-ggplot(m.roc.df,aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005))

@@

miseq.roc.p<-ggplot(m.roc.df,aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))#+scale_x_continuous(limits=c(0,0.005)

@@

Hiseq.roc<-ggplot(subset(h.roc.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005));Hiseq.roc

@@

Hiseq.roc.4<-ggplot(subset(h.roc.df,gc==4),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005));Hiseq.roc

@@

mapq_phred.normal<-ggplot(subset(sig.df,category %in% c(T,F) & gc==5),aes(x=Phred,y=MapQ,color=category))+geom_point(alpha=1)+geom_hline(yintercept=20)+geom_vline(xintercept=30)+scale_x_continuous(limits=c(30,40))+scale_color_hue(name="",labels=c("False posivite","True positive"))

@@

mapq_phred.stingy<-ggplot(subset(sig.df,category %in% c(T,F) & gc==5),aes(x=Phred,y=MapQ,color=category))+geom_point(alpha=1)+scale_x_continuous(limits=c(30,40))+geom_hline(yintercept=30)+geom_vline(xintercept=35)+scale_color_hue(name="",labels=c("False positive","True positive"))

@@

mapq_phred.roc<-ggplot(subset(h.cut.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005))

@@

read.roc<-ggplot(subset(h.cut.read.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005))

@@

ggplot(subset(lofreq.roc,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab("1-Specificity (adjusted)")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005))

@@

## Figure 5 Lower inputs
### 10^4
```{r,roc_lower_inputs4}
roc.4<-ggplot(subset(h.cut.read.df,gc==4),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005))

@@

### 10^3
```{r,roc_lower_inputs3}
roc.3<-ggplot(subset(h.cut.read.df,gc==3),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005))

@@

dups.roc.p<-ggplot(dups.roc,aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("1-Specificity")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005))

@@

>>>>

  #plot the roc
  roc.p<-ggplot(roc.df,aes(x=1-specificity,y=sensitivity))+geom_step(color="black",size=2)+xlab("False Positive Rate")+ylab("Sensitivity")+theme(axis.title.y=element_text(vjust=1))
  roc.p<-roc.p+geom_line(data=lines,aes(x=spec,y=sense,color=as.factor(group)),size=c(1.5),lty=c(2))+scale_color_brewer(palette="Set1")

@@

}
plot.ex(0.35,0.95,roc.df,example)
pdf("~/Box Sync/Lab_work/Talks/2016_812/figures/roc.ex.pdf",width = 12,height = 8)
plot.ex(0.35,0.95,roc.df,example)
dev.off()

@@

miseq.roc.p<-ggplot(m.roc.df,aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab(bquote("False Positive Rate (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5))

@@

miseq.roc.p<-ggplot(m.roc.df,aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab("False Positive Rate")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))#+scale_x_continuous(limits=c(0,0.005)

@@

Hiseq.roc<-ggplot(subset(h.roc.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("False Positive Rate (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5));Hiseq.roc

@@

Hiseq.roc.4<-ggplot(subset(h.roc.df,gc==4),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab("False Positive Rate")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005));Hiseq.roc.4

@@

mapq_phred.normal<-ggplot(subset(sig.df,category %in% c(T,F) & gc==5),aes(x=Phred,y=MapQ,color=category))+geom_point(alpha=1)+geom_hline(yintercept=20)+geom_vline(xintercept=30)+scale_x_continuous(limits=c(30,40))+scale_color_hue(name="",labels=c("False posivite","True positive"))+ylab("Mapping Quality")+xlab("Base Qualtiy (Phred) ")

@@

mapq_phred.stingy<-ggplot(subset(sig.df,category %in% c(T,F) & gc==5),aes(x=Phred,y=MapQ,color=category))+geom_point(alpha=1)+scale_x_continuous(limits=c(30,40))+geom_hline(yintercept=30)+geom_vline(xintercept=35)+scale_color_hue(name="",labels=c("False positive","True positive"))+ylab("Mapping Quality")+xlab("Base Qualtiy (Phred) ")

@@

mapq_phred.roc<-ggplot(subset(h.cut.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("False Positive Rate (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5))

@@

read.roc<-ggplot(subset(h.cut.read.df,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("False Positive Rate (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5))

@@

ggplot(subset(lofreq.roc,gc==5),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1")+xlab("False Positive Rate (adjusted)")+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005))

@@

## Figure 5 Lower inputs
### 10^4
```{r,roc_lower_inputs4}
roc.4<-ggplot(subset(h.cut.read.df,gc==4),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("False Positive Rate (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5))

@@

### 10^3
```{r,roc_lower_inputs3}
roc.3<-ggplot(subset(h.cut.read.df,gc==3),aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("False Positive Rate (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005))

@@

dups.roc.p<-ggplot(dups.roc,aes(x=1-adj.specificity,y=adj.sensitivity))+geom_step(aes(color=exp.freq),size=2)+scale_color_brewer(palette = "Set1",name="Frequency",labels=c("5.0%","2.0%","1.0%","0.5%","0.2%"))+xlab(bquote("False Positive Rate (x"~10^-3~")"))+ylab("Sensitivity")+guides(color=guide_legend(title="Frequency"))+scale_y_continuous(limits=c(0,1))+scale_x_continuous(limits=c(0,0.005),breaks=c(0,0.001,0.002,0.003,0.004,0.005),labels=c(0:5))

@@

exp.meas.freq<-ddply(cut.df,~exp.freq+mutation+category, function(x){
                                                                                      freq1=x$freq.var[x$dup=="1"]
                                                                                      freq2=x$freq.var[x$dup=="2"]
                                                                                      if(length(freq1)==0) freq1=0
                                                                                      if(length(freq2)==0) freq2=0
                                                                                      out=data.frame(freq1=freq1,freq2=freq2)})

ggplot(subset(exp.meas.freq),aes(x=freq1,y=freq2,color=category))+geom_point(aes(size=3))+scale_y_log10()+scale_x_log10()+xlab("Frequency in sample 1")+ylab("Frequency in sample 2")+scale_color_hue(name="",labels=c("False positive","True positive"))+theme(legend.position=c(0.5,0.95))+geom_abline(intercept=0,slope=1,lty=2)->dup.freq
dup.freq

pdf("~/Box Sync/Lab_work/Talks/2016_812/figures/dup.freq.pdf")
dup.freq
dev.off()
